Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex

\newcommand{\langName}[0]{TinyML\textsuperscript{2}}
\newcommand{\origLang}[0]{CoreML\textsuperscript{2}}
\newcommand{\typeRule}[3]{#1 \vdash #2 \colon #3}
\newcommand{\guards}[0]{\lhd}
\newcommand{\lift}[1]{\lfloor #1 \rfloor}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}

@@

Our language and proof, \langName, are a simplified version of what is
presented in Simonet and Pottier's work on information flow for an ML-like
language, \origLang~\cite{InfoFlowML}.  The proof proceeds by designing a
core language, extending it with a term that represents a ``pair'' of 
values varied across two executions, and introducing these ``pairs'' of 
values in contexts where the value would have a high-security label.
The proof then becomes a matter of showing that if
the program is typed with a low security label, it does not terminate
with a result that is an instance of one of these ``pairs.''

@@

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states (answers) in the language are
now simple values because there are no exceptions.

@@

    As seen in Figure~\ref{fig:syntax}, we have a slightly different syntax
    structure for \langName ~than was seen in~ \origLang.  Specifically, we constructed
    values, answers, and expressions explicitly to not allow nesting of
    bracketed values.  The syntax defined by Simonet and Pottier did allow
    for this nesting, and authors dismissed is as a non-sensible
    construction.  Unfortunately, allowing such syntactic nesting 
    prevents the completeness Lemma from being proveable.
    Realizing that our definitions did not disallow
    this by construction after running into issues in the proof, we were able to
    fix the definition, producing what is in Figure~\ref{fig:syntax}.

@@

    Proving our own version of Lemma~\ref{lem:soundness} was uniquely
    instructive because it forced us to recognize that the original
    formulation in Simonet and Pottier's paper on \origLang ~wasn't 
    correct as stated.  Simonet and Pottier's Lemma asserts that 
    if $e \rightarrow e'$, then $\lift{e}_i \rightarrow \lift{e'}_i$.
    This does not hold in the case where $e$ is of the form $<v1 | v2> v$;
    In this case, the single reduction rule that applies is \ref{eq:lift-app},
    which does not step $\lift{e}_i \rightarrow \lift{e'}_i$ for any $i$ 
    (as $\lift{e}_i$ and $\lift{e'}_i$ are identical).  Luckily, we are
    fairly confident, given that we were still able to prove
    Lemma~\ref{lem:stuck_bracket} despite this change, that this is not a
    critical error in the original paper.
\end{description}

>>>>

\newcommand{\langName}[0]{TinyML\textsuperscript{2}~}
\newcommand{\origLang}[0]{CoreML\textsuperscript{2}~}
\newcommand{\typeRule}[3]{#1 \vdash #2 \colon #3}
\newcommand{\guards}[0]{\lhd}
\newcommand{\lift}[1]{\lfloor #1 \rfloor}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}

@@

Our language and proof, \langName, are a simplified version of what is
presented in Simonet and Pottier's work on information flow for an ML-like
language, \origLang \cite{InfoFlowML}.  The proof proceeds by designing a
core language, extending it with a term that represents a ``pair'' of 
values varied across two executions, and introducing these ``pairs'' of 
values in contexts where the value would have a high-security label.
The proof then becomes a matter of showing that if
the program is typed with a low security label, it does not terminate
with a result that is an instance of one of these ``pairs.''

@@

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states (answers) in the language are
now simple values.

@@

    As seen in Figure~\ref{fig:syntax}, we have a slightly different syntax
    structure for \langName than was seen in~ \origLang.  Specifically, we constructed
    values, answers, and expressions explicitly to not allow nesting of
    bracketed values.  The syntax defined by Simonet and Pottier did allow
    for this nesting, and authors dismissed is as a non-sensible
    construction.  Unfortunately, allowing such syntactic nesting 
    prevents the completeness Lemma from being proveable.
    Realizing that our definitions did not disallow
    this by construction after running into issues in the proof, we were able to
    fix the definition, producing what is in Figure~\ref{fig:syntax}.

@@

    Proving our own version of Lemma~\ref{lem:soundness} was uniquely
    instructive because it forced us to recognize that the original
    formulation in Simonet and Pottier's paper on \origLang wasn't 
    correct as stated.  Simonet and Pottier's Lemma asserts that 
    if $e \rightarrow e'$, then $\lift{e}_i \rightarrow \lift{e'}_i$.
    This does not hold in the case where $e$ is of the form $<v1 | v2> v$;
    In this case, the single reduction rule that applies is \ref{eq:lift-app},
    which does not step $\lift{e}_i \rightarrow \lift{e'}_i$ for any $i$ 
    (as $\lift{e}_i$ and $\lift{e'}_i$ are identical).  Luckily, we are
    fairly confident, given that we were still able to prove
    Lemma~\ref{lem:stuck_bracket} despite this change, that this is not a
    critical error in the original paper.
\end{description}
